Plots for Latent Hawkes Paper

### 2020-11-18 output_scripts/Paper_Plots.Rmd
add figure 5b sim spearman rank and attempt to modify plot 8b to be clearer

# Figure 5b: Simulation Spearman Rank

@@

#png(paste(plot_path,"real_predict_N_all_cohort.png",sep=""),width=600,height=300)
p4 <- ggplot(temp_plot_df, aes(x=day, y=avg, group=method, color=method)) + 
  geom_line(size=1.2, alpha=0.8, position=position_dodge(0.2)) +
  geom_errorbar(aes(ymin=avg-sd, ymax=avg+sd), width=0.8, size=0.8, alpha=0.8,
                 position=position_dodge(0.2)) +
  scale_color_manual(values = viridis::viridis(5)) + 
  ggtitle("(b)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_text(size = 18)) +
  xlab("Prediction horizon (day)") + 
  ylab("Frobenius norm of error") + 
  coord_cartesian(ylim=c(2.5,57.5)) + 
  guides(color=guide_legend(title="Model")) 
p4
```

>>>>

# Figure 5b: Simulation Spearman Rank
```{r fig-5b-spearman-sim}
sim_files <- list.files(here("output", "rank_sims",
                             "sims_m3_dc_isi_sparse"))

all_sims <- list()
for(i in seq_along(sim_files)) {
 single_fit <- readRDS(here("output", "rank_sims", 
                            "sims_m3_dc_isi_sparse",
                            sim_files[i]))
 all_sims[[i]] <- single_fit
}

spear <- function(sim_data) {
  truth <- sim_data$truth
  sim_data %>%
    select(m1:glicko) %>%
    map( ~cor.test(truth, .x,
                   method = "spearman")$estimate  ) %>%
    enframe() %>%
    unnest(cols = c(value))
}

sim_data <- map_dfr(all_sims, spear)

name <- sim_data$name

sim_data$name <- case_when(
          name == "isi" ~ "I&SI",
          name == "m1" ~ "C-HP",
          name == "m2" ~ "C-DCHP",
          name == "m3_dc" ~ "C-MMHP",
          name == "agg" ~ "AggRank",
          name == "glicko" ~ "Glicko")

sim_data$name <- factor(sim_data$name, levels = c("I&SI",
                                                  "AggRank",
                                                  "Glicko",
                                                  "C-HP",
                                                  "C-DCHP",
                                                  "C-MMHP"))

sim_data %>% 
  rename(Method = name, corr = value) %>%
  ggplot(aes(Method,corr)) + geom_boxplot(aes(fill = Method)) +
  scale_fill_manual(values = viridis::viridis(6)) +
  labs(y = "Rank Correlation") + theme_bw()
```

@@

#png(paste(plot_path,"real_predict_N_all_cohort.png",sep=""),width=600,height=300)
p4 <- ggplot(temp_plot_df, aes(x=day, y=avg, group=method, color=method)) + 
  geom_line(aes(linetype = method),
            size=1.2, alpha=0.8, position=position_dodge(0.2)) +
  geom_errorbar(aes(ymin=avg-sd, ymax=avg+sd), width=0.8, size=0.8, alpha=0.8,
                 position=position_dodge(0.2)) +
  scale_color_manual(values = viridis::viridis(5)[1:5]) + 
  ggtitle("(b)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_text(size = 18)) +
  xlab("Prediction horizon (day)") + 
  ylab("Frobenius norm of error") + 
  coord_cartesian(ylim=c(2.5,57.5)) + 
  guides(color=guide_legend(title="Model")) +
  guides(linetype = FALSE)
p4
```
